Parsing Postfix log files

### 2009-03-09 doc/logparser-background.tex
Improved checks, added a check, dropped a check, and made corrections based on the new check.

\begin{verbatim}
  main.cf:
  smtpd_client_restrictions =
    ...
    permit_sasl_authenticated,
    check_client_access /etc/postfix/allow_webserver.cidr,
    ...

@@

\begin{verbatim}
  main.cf:
  smtpd_client_restrictions =
    ...
    check_client_access /etc/postfix/require_dns_entries.cidr,
    ...

>>>>

\begin{verbatim}
  main.cf:
  smtpd_client_restrictions =
    <other restrictions>
    permit_sasl_authenticated,
    check_client_access /etc/postfix/allow_webserver.cidr,
    <other restrictions>

@@

\begin{verbatim}
  main.cf:
  smtpd_client_restrictions =
    <other restrictions>
    check_client_access /etc/postfix/require_dns_entries.cidr,
    <other restrictions>

### 2009-03-09 doc/logparser-implementation.tex
Improved checks, added a check, dropped a check, and made corrections based on the new check.

    \item [delays] More details information about how long the mail was
        delayed for while it was being delivered  This will only be present
        for delivered mails..

>>>>

    \item [delays] More details information about how long the mail was
        delayed for while it was being delivered  This will only be present
        for delivered mails.
